\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2015-02-27 paper2015asml.tex
close to final version

%EDITING COMMANDS
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
\newcommand{\todo}{\colorbox{red}{TODO}}
\newcommand{\tj}[1]{\ensuremath{\xi_\text{#1}}}

@@

We extended the MoveIt! benchmarking architecture~\cite{cohen2012generic} with video generation capabilities to automate the generation of a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (Fig.~\ref{fig:scenes}): a kitchen (Countertop), an industrial workbench (Industrial) and a drawer on a table (Drawer). Multiple queries were generated in each scene for trajectories of the right arm of the PR2 robot (Fig.~\ref{fig:PR2}. The robot was positioned in the scenes manually and motion planning queries were constructed by hand. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

@@

Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances. \hl{These features are used because of their applicability for comparing trajectories from location based services}~\cite{chen2013dynamic}.

@@

The dataset we have collected and the analysis we have already done in this paper will serve as a
 platform for further development of the idea of using 
a data-driven approach to motion planning. We intend to attempt to learn a cost function for describing the relation between the features and 
the ratings of the generated trajectories using inverse reinforcement learning. We hope to examine whether a cost function derived in this manner will 
lead to generation of more preferred trajectories.

>>>>

%EDITING COMMANDS
\newcommand{\hilight}[1]{\colorbox{yellow}{#1}}
\renewcommand{\hl}[1]{{#1}}
\newcommand{\todo}{\colorbox{red}{TODO}}
\newcommand{\tj}[1]{\ensuremath{\xi_\text{#1}}}

@@

We extended the MoveIt!~\cite{MoveIt} benchmarking architecture~\cite{cohen2012generic} with video generation capabilities to automate the generation of a large number of trajectories. The MoveIt! architecture allows for the definition of environments, referred to as planning scenes, start and goal states for robots (motion planning queries). It also allows for the use of any supported planning algorithms (planners). A combination of different scenes, motion queries, and planners was used to generate robot trajectories for evalutation. We chose three distinct scenes (Fig.~\ref{fig:scenes}): a kitchen (Countertop), an industrial workbench (Industrial) and a drawer on a table (Drawer). Multiple queries were generated in each scene for trajectories of the right arm of the PR2 robot (Fig.~\ref{fig:PR2}. The robot was positioned in the scenes manually and motion planning queries were constructed by hand. The positioning in the scenes was done with the expectation that the planning queries would not be impossible or trivial for the planning algorithms to solve.

@@

We computed the correlation between observer ratings of smoothness vs. the measured smoothness of the trajectories (Table~\ref{tab:corr_smoothness}). Note that higher values of the measured smoothness feature  indicate that the trajectories are jagged or non-smooth. The correlation between the smoothness rating and the measured smoothness is not very high, indicating that human observer perception of smoothness is different from the particular measure that we used for the robot trajectories. A likely explanation is that excessive motions of the wrist (while still measured as smooth) are perceived as non-smooth by the human observer. We also computed the correlation between path lengths and the efficiency rating assigned by the human observer (Table~\ref{tab:path_length}). Here, the correlation was high (the negative value of the correlation coefficients indicate that higher path lengths are perceived as less efficient).

\begin{table}
\centering
\begin{tabular}{|p{1.25cm}|c|c|c|c|}
\hline
& Class & Smoothness & Smoothness & Smoothness \\ 
& Smooth & (Joint) & (Tool) & (Wrist) \\ \hline
Class Smooth & 1 & -0.27 & -0.29 & -0.38 \\ \hline
Smoothness (Joint) & -0.27 & 1 & 0.68 & 0.62 \\ \hline
Smoothness (Tool) & -0.29 & 0.68 & 1 & 0.87 \\ \hline
Smoothness (Wrist) & -0.38 & 0.62 & 0.87 & 1 \\ \hline
\end{tabular}
\caption{Correlation between human observed rating for smoothness and measured smoothness values for the trajectories.}
\label{tab:corr_smoothness}
\vspace{-0.1in}
\end{table}

\begin{table}
\centering
\begin{tabular}{|p{1.25cm}|c|c|c|c|}
\hline
& Class & Path Length & Path Length & Path Length \\ 
& Efficient & (Joint) & (Wrist) & (Tool) \\ \hline
\hline
Class Efficient & 1 & -0.79 & -0.8 & -0.76 \\ \hline
Path Length (Joint) & -0.79 & 1 & 0.89 & 0.86 \\ \hline
Path Length (Wrist) & -0.8 & 0.89 & 1 & 0.97 \\ \hline
Path Length (Tool) & -0.76 & 0.86 & 0.97 & 1 \\ \hline
\end{tabular}
\caption{Correlation between human observed rating for efficiency and measured path lengths for the trajectories.}
\label{tab:path_length}
\vspace{-0.1in}
\end{table}

@@

Next, we compute comparison features between $\xi_{\text{BFS}}$ and three workspace trajectories for the elbow ($\xi_\text{elbow}$), wrist ($\xi_\text{wrist}$) and finger-tip ($\xi_\text{tip}$) links. The comparison features computed between each pair of trajectories are the Hausdorff distances~\cite{dubuisson1994modified} and Dynamic Time Warping~\cite{senin2008dynamic} distances. \hl{These features have also often been used for comparing trajectories in applications like location based services and are useful in comparing trajectories that might have different lengths or shapes.}~\cite{chen2013dynamic}.

@@

The dataset we have collected and the analysis we have already done in this paper will serve as a
 platform for further development of the idea of using 
a data-driven approach to motion planning. We intend to attempt to learn a cost function for describing the relation between the features and 
the ratings of the generated trajectories using inverse reinforcement learning (e.g. as in~\cite{kalakrishnanICRA2013},~\cite{abbeel2004apprenticeship}). We hope to examine whether a cost function derived in this manner will 
lead to generation of more preferred trajectories.
